\Large \bf On semidefinite-representable sets over valuation fields

### 2025-05-23 article/paper_padic_spec.tex
encore intro

Contrary to the LP case, the complexity status of SDP is widely open. In a fixed-precision model of computation, SDP is solvable in polynomial time in the input size (matrix size, number of variables, bit size of the coefficients), in $\log(\frac{1}{\varepsilon})$ (where $\varepsilon$ is the precision) and $\log(\frac{R}{r})$, where $r,R$ are radii of balls respectively included in and containing the feasible set, cf. \cite{grotschel1981ellipsoid} or \cite[Thm.1.1]{de2016turing} (see also \cite[Sec.1.9]{deKlerk}). In exact arithmetic, complexity bounds are known based either on general quantifier elimination \cite{ramana1997exact,porkolab1997complexity} or by means of a dedicated application of the critical point method exploiting the determinantal structure of the constraints \cite{henrion2016exact,NALDI2018206}.

In this paper we consider the situation where input data are defined over fields $K$ with a prescribed valuation map $\val$ on $K$. The main example is the field of $p$-adic numbers with $p$-adic valuation.

>>>>

Contrary to the LP case, the complexity status of SDP is widely open. Ramana's construction \cite{ramana1997exact} implies a series of general results: in the Blum-Shub-Smale real numbers machines model \cite{blum1989theory}, the feasibility of SDP is in $\text{NP} \cap \text{co-NP}$, whereas it is not known to be in NP in the Turing model; checking boundedness, attainability and optimality can be polynomially reduced to the feasibility of SDP \cite{ramana1997exact}.

Assuming the input data belongs to an effective field $K$ (\emph{e.g.} $K = \QQ$) then a solution can be described and computed as element of a vector space over some algebraic extension of $K$. For exact computation, complexity bounds are known based either on general quantifier elimination \cite{ramana1997exact,porkolab1997complexity} and explicit algorithms exist based on a dedicated application of the so-called critical point method, and exploiting the determinantal structure of the constraints \cite{henrion2016exact,NALDI2018206}.

A complexity analysis for the computation of an approximate solution of an SDP can be made based on the ellipsoid algorithm \cite{khachiyan1979polynomial,grotschel1981ellipsoid} or on interior-point methods \cite{de2016turing}; in this approximation framework, SDP is solvable in polynomial time in the input size (\emph{i.e.} matrix size, number of variables, bit size of the coefficients), $\log(\frac{1}{\varepsilon})$ (where $\varepsilon$ is the target precision) and $\log(\frac{R}{r})$, where $r,R$ are radii of balls respectively included in and containing the feasible set, cf. \cite{grotschel1981ellipsoid} or \cite[Thm.1.1]{de2016turing} (see also \cite[Sec.1.9]{deKlerk}).

In this paper we consider the situation where input data are defined over fields $K$ with a prescribed valuation map $\val$ on $K$. The main example is the field of $p$-adic numbers with $p$-adic valuation. \todo{Give motivations for p-adic precision of LP/SDP.}
